\vspace{-.2in} Squint: Lossy Hierarchical Compression on Symbol Streams \vspace{-.1in}

### 2012-12-12 tex/paper.tex
Moar table fixin'

\begin{algorithm}[h]
\caption{Similarity Lossifier Algorithm}
\label{sim_alg}
\begin{algorithmic}[1]
\Procedure{Lossify-Sim}{$g$} \Comment{Simplify grammar g}
  \While{there are similar variables to replace}
    \For{$var_1 \rightarrow rhs_1,\ var_2 \rightarrow rhs_2 \in g$}
      \State $str_{i} \gets expand(rhs_i)$
      \If{$lsim(str_{1},str_{2})<\epsilon$}
        \State replace the longer var with the smaller throughout $g$
        \State break
      \EndIf
    \EndFor
  \EndWhile
\EndProcedure
\end{algorithmic}
\end{algorithm}

@@

The previous algorithm updates the grammar sequentially, since each variable
replacement can have an effect on large parts of the grammar, we will have to
go through comparing all pairs again after the change.  An alternative
algorithm would be to try to replace similar variables in parallel. This would
avoid many of the repeat pair-comparisons done in \Similarity. In other
words, the algorithm below puts similar variables into equivalence class
clusters, and then replaces each variable in a cluster them with the smallest
representative all at once each iteration.

@@

In both datasets, the compression ratios achieved for both algorithms are
roughly equal given the same value for $\epsilon$, so it is fair to compare the
algorithms for the same values of $\epsilon$.  From plotting the data, we see
that runtime of the algorithms are roughly polynomial in the size of the data,
so we can perform a linear regression on the log-log transform of the data to
find the exponents $\alpha$ for the runtime $r(n)=n^\alpha$ where $n$ is the
length of the input string. In the charts below, all of the linear regressions
had $R^2$ values of over $0.98$.

\begin{tabular}{l|l|l|l|l}
rep-n runtime & Sim: $\epsilon=.4$ & Sim: $\epsilon=.2$ & Clust: $\epsilon = .4$ & Clust: $\epsilon = .2$ \\
Exponent      & $1.859$ & $2.026$ & $1.306$ & $1.305$
\end{tabular}

\begin{tabular}{l|l|l|l|l}
gen-n runtime & Sim: $\epsilon=.4$ & Sim: $\epsilon=.2$ & Clust: $\epsilon = .4$ & Clust: $\epsilon = .2$ \\
Exponent      & $2.629$ & $2.493$ & $1.814$ & $2.061$
\end{tabular}

@@

The second piece of text is one of the entries to this year's International
Obfuscated C code contest, at \url{http://www.ioccc.org/2012/deckmyn/deckmyn.c}
.  The size of the lossified grammar is 1576 compared with the original size of
1973. The intricate whitespacing was lost, but the clear delineation into
sections was kept, key words such as `define' and `for' are very visible, and
the texture of the obfuscated C is very obvious.

@@

\subsection*{Output:}

>>>>

\begin{algorithm}[h]
\caption{Similarity Lossifier Algorithm}
\label{sim_alg}
\begin{algorithmic}[1]
\Procedure{Lossify-Sim}{$g$} \Comment{Simplify grammar g}
  \While{there are similar variables to replace}
    \For{$var_1 \rightarrow rhs_1,\ var_2 \rightarrow rhs_2 \in g$}
      \State $str_{i} \gets expand(rhs_i)$
      \If{$lsim(str_{1},str_{2})<\epsilon$}
        \State replace the larger var with the smaller throughout $g$
        \State break
      \EndIf
    \EndFor
  \EndWhile
\EndProcedure
\end{algorithmic}
\end{algorithm}

@@

The previous algorithm updates the grammar sequentially, since each variable
replacement can have an effect on large parts of the grammar, we will have to
go through comparing all pairs again after the change.  An alternative
algorithm would be to try to replace as many similar variables as possible
all in one sweep. This would
avoid many of the repeat pair-comparisons done in \Similarity. In other
words, the algorithm below puts similar variables into equivalence class
clusters, and then replaces each variable in a cluster them with the smallest
representative all at once each iteration.

@@

In both datasets, the compression ratios achieved for both algorithms are
roughly equal given the same value for $\epsilon$, so it is fair to compare the
algorithms for the same values of $\epsilon$.  From plotting the data, we see
that runtime of the algorithms are roughly polynomial in the size of the data,
so we can perform a linear regression on the log-log transform of the data to
find the exponents $\alpha$ for the runtime $r(n)=n^\alpha$ where $n$ is the
length of the input string. In the charts below, all of the linear regressions
had $R^2$ values of over $0.98$.
\begin{align*}
  \text{rep-n:}\quad
  \begin{array}{l|l|l||l|l}
    & \multicolumn{2}{c||}{\Similarity} & \multicolumn{2}{c}{\Cluster} \\ \hline
    \epsilon & .4 & .2 & .4 & .2 \\
    \alpha   & 1.859 & 2.026 & 1.306 & 1.305
  \end{array}
  &&
  \text{gen-n:}\quad
  \begin{array}{l|l|l||l|l}
    & \multicolumn{2}{c||}{\Similarity} & \multicolumn{2}{c}{\Cluster} \\ \hline
    \epsilon & .4 & .2 & .4 & .2 \\
    \alpha   & 2.629 & 2.493 & 1.814 & 2.061
  \end{array}
\end{align*}

@@

The second piece of text is one of the entries to this year's International
Obfuscated C code contest, at \url{http://www.ioccc.org/2012/deckmyn/deckmyn.c}
. We believe this is a particularly good example since its structure is foreign,
but still discernable. Whitespace is particularly important in standard english
but our lossifiers don't treat it any differently from any other symbol.
The size of the lossified grammar is 1576 compared with the original size of
1973. The intricate whitespacing was lost, but the clear delineation into
sections was kept, key words such as `define' and `for' are very visible, and
the texture of the obfuscated C is very obvious. For instance, after the
distinct `#define' headers, the first sections has a bunch of control statements
like `for' and `if', while the middle sections have very generous spacing
and many repeated pointer derence operators such as `***'. Both of these
kinds of textures are retained after lossifying.

@@
